Manuscript title here

### 2024-09-20 manuscript.Rmd
glömde lägga till en källa

One way to improve trauma care quality is trough identifying Opportunities for Improvement (OFI). This method has an advantage compared to traditional mortality reviews in that it also includes non-fatals. There are different processes to finding OFIs, but one of the primary ways is structured multidisciplinary morbidity and mortality reviews of patient cases [källa 8]. In order for the review content to be as comprehensive as possible for trauma care, the Donabedian quality of care framework can be used[@donabedian_quality_1988]. It is based on the three factors of structure, process and outcome. By following this framework, healthcare providers will be able to systematically find and address OFIs[källa?]. This will in turn improve the effectiveness of trauma care, directly impacting mortality and morbidity[källa?/8].

>>>>

One way to improve trauma care quality is trough identifying Opportunities for Improvement (OFI). This method has an advantage compared to traditional mortality reviews in that it also includes non-fatals. There are different processes to finding OFIs, but one of the primary ways is structured multidisciplinary morbidity and mortality reviews of patient cases [@world_health_organization_guidelines_2009]. In order for the review content to be as comprehensive as possible for trauma care, the Donabedian quality of care framework can be used[@donabedian_quality_1988]. It is based on the three factors of structure, process and outcome. By following this framework, healthcare providers will be able to systematically find and address OFIs[källa?]. This will in turn improve the effectiveness of trauma care, directly impacting mortality and morbidity[källa?/8].
